---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ec1027

<!-- badges: start -->
<!-- badges: end -->

This package provides datasets and some functions to be used in the course EC1027 - Econometrics I.

## Installation

<!--
You can install the released version of ec1027 from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("ec1027")
```
-->

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("jcpernias/ec1027")
```

## Datasets

The `ec1027` package provides some datasets taken from Jeffrey M. Wooldridge (2006:) 
*Introductory econometrics : a modern approach*, 3rd ed., Thomson South-Western:

* `bwght`: Birth weight and cigarette smoking.

* `earns`: Earnings, productivity and hours (macro).

* `gpa1`: Gollege GPA and its predictors.

* `hprice1`: House prices and characteristics.

* `hseinv`: Housing investment and prices.

* `intdef`: Interest rates and Federal budget balance.

* `rdchem`: R & D and sales, chemical industry.

* `traffic2`: Speed limits and highway safety.

Note that the package [wooldridge](https://justinmshea.github.io/wooldridge/) provides access to many more datasets. Also note that derived variables (logarithms, lags, etc) are not included in the `ec1027` data sets.

## Example

Load the `ec1027` package and use `data` to bring one of the included data sets to the global environment.
```{r}
library(ec1027)

## data on house prices
data(hprice1)

## Show the first observations
head(hprice1)
```


## Code

### Robust standard errors

Several functions have an `vce` parameter that allows the use of variance covariance estimators consistent in the presence of heteroskedasticity or autocorrelation. 

Output from regression models is usually examined with the `summary` function:
```{r}
mod <- lm(price ~ sqrft + bdrms + colonial, data = hprice1)

summary(mod)
```
But `summary` only shows the OLS standard errors of estimates. The `coef_table` function produces output similar to `summary` but allows other covariance matrix estimators:
```{r}
# Heteroskedasticity consistent errors
coef_table(mod, vce = "HC")
```

Also, the `se` function computes standard errors robust to heteroskedasticity and autocorrelation. See more details in the documentation of this function.


### Heteroskedasticity tests

The function `white_test` computes White's test for heteroskedasticity:
```{r}
white_test(mod)
```

The function `het_test` computes LM tests for heteroskedasticity that allow the user to specify the variables related to hetroskedasticity.
```{r}
# Using all covariates
het_test(mod)

# Using only sqrft and colonial
het_test(mod, ~ sqrft + colonial)
```



### Hypotheses tests

The `drop_test` function performs a Wald test of the null joint hypotheses that the parameters of some variables are 0.
The `vce` argument allows the use of alternative covariance matrix estimators.
```{r}
# Joint significant test with the OLS covariance matrix estimator
drop_test(mod)

# Now using a heteroskedasticity consistent covariance matrix estimator
drop_test(mod, vce = "HC")

# Heteroskedasticity robust rest test on the joint signifinace of 
# bdrms and colonial
drop_test(mod, ~ bdrms + colonial, vce = "HC")
```



